---
title: "Boston Data (1978)"
author: "Jack Lovell"
date: "2/10/2021"
output:
  ioslides_presentation:
    highlight: MLR Model
    widescreen: yes
    smaller: yes
---

## Agenda

- Variables (predictors consist of continuous data and a factor)
- medv: median property value in $1000s (Y-variables --response)
- rm: number of rooms (P1) (cont.)
- crim: per captia crime rate by town (P2) (cont.)
- rad: index of accessibility to highways (Factor) (P3) (cat.)

```{r Loading Boston Data}
library(MASS)
data(Boston)
```

## Look at the first few rows of the data, the structure, table of counts for rad

```{r}
head(Boston)
str(Boston)
table(Boston$rad)
```
## Fit model and look at results

```{r}
m_medv <- lm(medv~rm+crim+factor(rad), data=Boston)
m_medv
```

Note: k-1 factors is because we need a refernce category.

## Estimated parameters

Note: rad1 has been omitted it is a reference category

**Write down the fitted model**

```{r}
#crim = 0.00632
#rad = 1
#rm = 6.575

-27.48-0.16*0.00632+7.91*6.575+0*8
```
```{r}
fitted_medv <- fitted.values(m_medv)
head(fitted_medv)
#IN SAMPLE PREDICTION
```


## Prediction 2: out of sample (given new obs)

- Predict some new x within the range of the data

- crim = 3.6
- rad = 5
- rm = 6.28

- Use 'predict()'

```{r}
predict(m_medv,data.frame(crim=3.6,rad="5",rm=6.28))
```

## given 2 sets of predictors

- crim      rad     rm
  3.6       5       6.28
  3.6       24      6.28
  
```{r}
newX <- data.frame(crim=c(3.6,3.6), rad=c("5","24"), rm=c(6.28,6.28))
predict(m_medv,newX)
```

## Question: Use the model to identify whether a property with crim = 3.6, rad = "5", rm = 6 with price 36k is fair

```{r}
newX <- data.frame(crim=3.6, rad="5", rm=6)
predict(m_medv,newX)
```
## Question: Use the model to identify whether a property with crim = 3.6, rad = "5", rm = 6 with price 36k is fair cont.

```{r}
# taking into account the uncertainty of prediction, we need what's called a predicition interval
predict(m_medv,newX, interval = "prediction", level = 0.95) # Y_prediction -- raw data
# taking into account the confidence interval 
predict(m_medv,newX, interval = "confidence", level = 0.95) # E[Y_prediction]
```

pvalue = 1-pchisq(T,n-1