---
title: "Untitled"
author: "Jack Lovell"
date: "1/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# stat 3400 01/27/2021
## BY Jack Lovell

** MLE REAL WORLD DATA **

### Goal for simulation

We would like to fit the data to a normal model and use MLE to find the mean and SD.

```{r load data}
data <- read.csv("https://git.io/v58i8")
```

### Step 1 Visualize observations

```{r}
hist(data$x)
plot(density(data$x))
```
### Step 2 Choose the model 

```
Normal model w/ parameters $\mu$ $\sigma$
```

### Step 3 Define likelihood function

```{r}
nll.normal <- function(data,par){return(-sum(log(dnorm(data, mean=par[1], sd=par[2]))))}
```

### Step 4 Find parameters

The parameters in our model are the mean and standard deviation that maximize the likelihood function

```{r}
optim(par = c(1,0.1), fn = nll.normal, data=data$x)
```

### Step 5 Check goodness of fit

```{r}
x = seq(-3.4,0.01)
plot(density(data$x))
lines(x, dnorm(x,mean=2.85, sd=0.12), lty=2)
```







